Attack-Tolerant Networks: A Structural, Multipath Approach

### 2016-08-03 wsdm-2017/source/paper.tex
Revise intro.

Large-scale communication networks, exemplified by the Internet,
have become ubiquitous, and are now crucial infrastructure for
individuals, communities, and organizations around the world.
As with any critical infrastructure, the cost of a failure can be
immense, so methods for tolerating various kind of faults are an
important and ongoing area of research
\cite{zin_survey_2015,albert_error_2000,sterbenz_resilience_2010}.
In fact, the decentralized design of the Internet was intended to protect
against targeted attacks, such as nuclear strikes
\cite{baran_distributed_1964}.
Such targeted attacks are formally described as {\em adversarial faults}
and are some of the most difficult to protect against.
Both theoretical results and recent events have demonstrated that
the Internet is surprisingly vulnerable to adversarial faults.
Decentralization remains a promising approach to building resilient networks,
but further work is needed to understand the relationship between
decentralized network structure and adversairal fault tolerance.

Many complex networks, including the Internet and World-Wide Web, exhibit
scale-free structure
\cite{barabasi_emergence_1999,barabasi_scale-free_2009}.
While scale-free networks tolerate random faults well,
they are highly susceptible to adversarial faults, i.e. attacks
\cite{albert_error_2000}.
For example, in 2008, YouTube suffered a worldwide outage for several hours
when a service provider in Pakistan advertised false routing information
\cite{hunter_pakistan_2008}.
The action (known as a {\em black hole attack}) was intended to censor YouTube
within Pakistan only, but resulted in a worldwide cascading failure.
Such vulnerabilities are not limited to any one system or protocol, but an
attribute of complex communication networks themselves.
General techniques for understanding and mitigating these vulnerabilities are
needed.

>>>>

Large-scale communication networks, exemplified by the Internet,
have become ubiquitous, and are now crucial infrastructure for
individuals, communities, and organizations around the world.
As with any critical infrastructure, the cost of a failure can be
immense, so methods for tolerating various kind of faults are an
important and ongoing area of research
\cite{zin_survey_2015,albert_error_2000,sterbenz_resilience_2010}.
In fact, the decentralized design of the Internet was intended to protect
against targeted attacks, such as nuclear strikes
\cite{baran_distributed_1964}.
Such targeted attacks are formally described as {\em adversarial faults}
and are some of the most difficult to protect against.
Both theoretical results and recent events (described below)
have demonstrated that
the Internet is surprisingly vulnerable to adversarial faults.
Decentralization remains a promising approach to building resilient networks,
but further work is needed to understand the relationship between
decentralized network structure and adversairal fault tolerance.

Analysis of the Internet's router network has shown that while it is remarkably
resilient against random faults,
it is highly susceptible to adversarial faults \cite{albert_error_2000}.
These results have been attributed to the scale-free structure of the Internet's
router network
\cite{barabasi_emergence_1999,barabasi_scale-free_2009}.
In scale-free networks and other networks with heavy-tail degree distributions,
random failures are highly likely to pick low-degree nodes, thus having
little effect,
while adversarial faults target the small number of high-degree nodes,
thus removing a large number of edges with each fault.
It may seem to be a contradiction that the Internet both be decentralized
and exhibit a heavy-tailed degree distribution.
This contradiction is resolved by observing that the Internet is decentralized
in its {\em protocols}, but somewhat centralized in its {\em network structure}.
In other words, the protocols of the Internet do not {\em require}
centralization, but centralization may still emerge from the socio-technical
processes that create its network structure.

For example, in 2008, YouTube suffered a worldwide outage for several hours
when a service provider in Pakistan advertised false routing information
\cite{hunter_pakistan_2008}.
The action (known as a {\em black hole attack}) was intended to censor YouTube
within Pakistan only, but resulted in a worldwide cascading failure.
Such vulnerabilities are not limited to any one system or protocol, but an
attribute of complex communication networks themselves.
General techniques for understanding and mitigating these vulnerabilities are
needed.
